Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-08-30 WRITEUP/ms.tex
w/ DR's comments, need to shrink abstract

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 (hereafter RXJ1131) at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXJ1131 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXJ1131 and the companion, respectively.
The gas mass fraction of $\sim$19\% inferred for RXJ1131 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, IR luminosity, and
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXJ1131.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% that is higher
than the local value
but consistent with other galaxies at this epoch, suggesting that the bulk of the black hole mass of RXJ1131 is already in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
%Studying the interplay between \SF and active galactic nucleus (AGN) activity across cosmic epochs is crucial to
%our understanding of the
%processes governing the formation and evolution of both the SMBHs and their host galaxies.
% Significant attention has been focused on studying the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs in recent studies of galaxy evolution.
% \citep{Wang10, Lamastra10, Hopkins+05, 06, DiMatteo+05a, Page11, Page12,Simpson12}
Many recent studies of galaxy evolution have been focused on investigating the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs \citep[e.g.,][]{DiMatteo05a,Alexander05a,Hopkins06b,Coppin08a,Page12a,Simpson12a,Lamastra13a}.
It is currently not well-understood when and how the supermassive black holes (SMBHs) and
stellar populations of present-day massive galaxies were assembled,
but it is clear that the co-moving \SF rate and the black hole accretion rate densities both
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
A leading explanation for this decline is the decrease in molecular gas content and
\SF efficiency \citep[e.g.,][]{Erb06a, CW13, Walter14a},
but direct molecular gas measurements at intermediate redshift
$(0.2\,<\,z\,<\,1)$ that could confirm this explanation remain largely limited to
spatially unresolved CO observations of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}. %18+15

Meanwhile, empirical scaling relations such as the
$M_{\rm BH}$$-$\mbulge relation \citep[e.g.,][]{Magorrian98a, HR04a}
have been established locally, suggesting a co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch
of \SF and AGN activity, have been made in recent years.
These studies find that
high-$z$ AGN host galaxies do not appear to follow the same $M_{\rm BH}$$-$\mbulge relation as nearby spheroidal galaxies. \citep[\eg][]{Walter04a,Borys05a, McLure06a,Peng06a, Riechers08a,Coppin08a,Alexander08a}.
Yet, the $M_{\rm BH}$$-$\mbulge relation remains poorly-constrained
at intermediate redshifts.
This is owed to the difficulties in
measuring stellar emission in quasar host galaxies which is typically
saturated by the sidelobes from their quasars.
With strong gravitational lensing, emission from the background quasar and its host galaxy originating from
different source-plane locations with different spatial extent is being magnified and stretched out inhomogenously,
allowing their emission to be
spatially resolved over more beams to reduce the dynamic range, and thus
measurements of the stellar emission in the host galaxy.

@@

In this paper, we present \bco and \cco line observations and
broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
study the properties of its molecular gas, the dust and stellar populations.
In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
In \Sec{results}, we report results for the \bco and \cco emission and broadband
photometry in RXJ1131.
In \Sec{anal}, we present lens modeling and dynamical modeling of the \bco data and
spectral energy distribution (SED) modeling of the photometric data.
In \Sec{diss}, we discuss
the ISM properties of the host galaxy of RXJ1131 and compare
them to other galaxy populations at low and high redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{HST (Archival)}
We obtained an {\it HST} image taken with
the ACS
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive.
The details of the observations can be found
in \citetalias{Claeskens06a}.
We apply astrometric correction to the optical image by adopting the VLA 5\,GHz map as the
reference coordinate frame.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is based on
its coordinates in the high-resolution optical image.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.

@@

We detect 2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved
emission which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
the background galaxy (RXJ1131).
The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
% assumes that the foreground galaxy is a point source, the...

@@

\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the source is resolved
$\gtrsim$2 resolution elements.
Given the extent of the lensed emission (see \Fig{CO21mom}),
this implies that we do not resolve
structures (e.g. knots and arcs) of the lensed emission
in our \bco data.
Nevertheless, the high spectral
resolution of these data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21mom}).
Hence, we reconstruct the intrinsic gas dynamics  % - morphology of different kinematic components - velocity structure
by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit
(\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
Our approach is similar to \citet{Riechers08a}, who reconstruct a source-plane
velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
whose host galaxy is also lensed into an Einstein ring configuration.
To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
that cover the full linewidth of $\sim$750\,\kms.

@@

Using the velocity dispersion ($\sigma$ = 30\,\kms) obtained by fitting a single Gaussian to the
de-lensed line profile of the companion and a
half-light radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from the best-fit lens model,  % redmost channel
we find a dynamical mass of
$M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun for the companion,
assuming an inclination angle of $i$\eq30$\degr$.
The uncertainty here only includes that of the CO source size.
On the other hand,
% we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
we find $M_{\rm dyn}$\,$\sin^2 30\degr$\,=\,5.8\E{8}\,\Msun
if we adopt the better-constrained $V$-band source size of $\sim$700\,pc \citepalias{Brewer08a}.
Since the $V$-band dynamical mass is substantially lower than the gas mass,
 the $V$-band emitting region may appear to be much smaller than its true extent due
to dust obscuration.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass, we find a galactic-scale %galaxy-wide
gas-to-dust ratio (GDR) of
40\pmm34.
This would be a factor of two higher if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
This GDR is lower than the statistical average of 206
in the \citetalias{Combes13a} sample but is well within the broad
range of values measured over their entire sample ($\sim$1$-$770).
Our ratio is also consistent with high-$z$ SMGs
% \citep[78\pmm26;][]{Bothwell13a}
\citep[]{Bothwell13a} and
local ULIRGs \citep{Wilson08a}, but lower than that of the Milky Way by
$\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.

@@

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the slight enhancement in sSFR suggests
that the \SF in RXJ1131 may be predominantly driven by interactions with the companion.

@@

Fitting dust SED models to the IR-to-mm photometry, we derive
a lensing-corrected dust mass of $M_{\rm dust}$\ssim4\E{8}\,\Msun,
an infrared luminosity of \LIR$\sim$\,1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun,
and a far-IR luminosity that corresponds to a SFR$_{\rm FIR}$\ssim120\,\sfrU.
These physical properties suggest that the merger system is dusty in nature with on-going \SF activity occuring
at a rate comparable to local ULIRGs/mergers and high-$z$ massive disk galaxies \citep{dacunha10a, Daddi10a}.
We also derive a stellar mass of $M_{*}$\ssim3\E{10}\,\Msun by fitting SED models to the
rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit to
account for differential lensing effect.
The source-plane distribution of the gas and stellar populations of different ages
indicates that the CO gas is of similar spatial extent as the old and long-lasting stellar populations,
whereas regions of recent \SF may be embedded within the molecular gas reservoir as a result of
gas accumulation driven by interactions with the companion.
Based on dynamical mass constraints, we cannot rule out the possibility that the
compact \SF in the host galaxy
may be heavily dust-obscured.
Hence, the true extent of recent \SF may be as extended as the molecular gas
reservoir.
While properties such as CO linewidth, SFR, and gas mass found in RXJ1131
are consistent with those of local ULIRGs and high-$z$ starburst galaxies,
its SFE is comparable to those of nearby and high-$z$ disk galaxies rather than
\SB systems. This is in good agreement with its disk-like kinematic signatures and its extended molecular gas distribution.
We find a specific \SF rate (sSFR\ssim4 Gyr\pmOne) that is $\lesssim$1.5$\sigma$ higher than those of ``main sequence'' galaxies.
The slight enhancement in sSFR suggests that
the on-going star formation in RXJ1131 could be driven by interactions with the companion.
Recent simulations have illustrated that the disk component of a gas-rich
progenitor galaxy with low SFE can be
retained upon merging since the efficiency at removing angular momentum of the gas via
gravitational torques provided by stellar components is reduced in such a system \citep{Springel05a, Robertson06a, Hopkins09a}.
% and the gas rapidly reform a cold disc in the background.
As such, the extended gas disk of RXJ1131 together with its low SFE may indicate
that the \SF in RXJ1131 could form a
larger stellar bulge in the merger remnant upon coalescing.

>>>>

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, IR luminosity, and
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
than the local value
but consistent with other galaxies at this epoch, suggesting that the bulk of the black hole mass of RXS\,J1131$-$1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
%Studying the interplay between \SF and active galactic nucleus (AGN) activity across cosmic epochs is crucial to
%our understanding of the
%processes governing the formation and evolution of both the SMBHs and their host galaxies.
% Significant attention has been focused on studying the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs in recent studies of galaxy evolution.
% \citep{Wang10, Lamastra10, Hopkins+05, 06, DiMatteo+05a, Page11, Page12,Simpson12}
Many recent studies of galaxy evolution have been focused on investigating the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs \citep[e.g.,][]{DiMatteo05a,Alexander05a,Hopkins06b,Coppin08a,Page12a,Simpson12a,Lamastra13a}.
It is currently not well-understood when and how the supermassive black holes (SMBHs) and
stellar populations of present-day massive galaxies were assembled,
but it is clear that the co-moving \SF rate and the black hole accretion rate densities both
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
A leading explanation for this decline is the decrease in molecular gas content and
\SF efficiency \citep[e.g.,][]{Erb06a, CW13, Walter14a},
but direct molecular gas measurements at intermediate redshift
$(0.2\,<\,z\,<\,1)$ that could confirm this explanation remain largely limited to
spatially unresolved CO observations of 
a modest sample of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}. %18+15

Meanwhile, empirical scaling relations such as the
$M_{\rm BH}$$-$\mbulge relation \citep[e.g.,][]{Magorrian98a, HR04a}
have been established locally, suggesting a co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch
of \SF and AGN activity, have been made in recent years.
These studies find that
high-$z$ AGN host galaxies do not appear to follow the same $M_{\rm BH}$$-$\mbulge relation as nearby spheroidal galaxies. \citep[\eg][]{Walter04a,Borys05a, McLure06a,Peng06a, Riechers08a,Coppin08a,Alexander08a}.
Yet, the $M_{\rm BH}$$-$\mbulge relation remains poorly-constrained
at intermediate redshifts due to the difficulty 
in separating the stellar component contributing to the optical emission from that of the bright AGN. 
This stems from the limited resolving power, which restricts the dynamic range that can be achieved at positions near the AGN.
Strong gravitational lensing provides the magnification necessary to spatially separate the AGN emission from the host galaxy stellar emission, significantly improving the dynamic range that can be achieved in studies of their host galaxies with current instruments.

@@

In this paper, we present \bco and \cco line observations and
broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
study the properties of its molecular gas, dust and stellar populations.
In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
In \Sec{results}, we report results for the \bco and \cco emission and broadband
photometry in RXJ1131.
In \Sec{anal}, we present lens modeling and dynamical modeling of the \bco data and
spectral energy distribution (SED) modeling of the photometric data.
In \Sec{diss}, we discuss
the ISM properties of the host galaxy of RXJ1131 and compare
them to other galaxy populations at low and high redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{HST (Archival)}
We obtained an {\it HST} image taken with
the ACS
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive.
The details of the observations can be found
in \citetalias{Claeskens06a}.
We apply an astrometric correction to the optical image by adopting the VLA 5\,GHz map as the
reference coordinate frame.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is based on
its coordinates in the high-resolution optical image.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.

@@

We detect 2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
the background galaxy (RXJ1131).
The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
% assumes that the foreground galaxy is a point source, the...

@@

\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the source is resolved
$\gtrsim$2 resolution elements.
Given the extent of the lensed emission (see \Fig{CO21mom}),
this implies that we do not resolve
structures (e.g. knots and arcs) of the lensed emission
in our \bco data.
Nevertheless, the high spectral
resolution of these data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21mom}).
Hence, we reconstruct the intrinsic gas dynamics  % - morphology of different kinematic components - velocity structure
by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit
(\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
Our approach follows a similar strategy as \citet{Riechers08a}, who reconstruct a source-plane
velocity gradient and constrain the gas dynamics in the $z$\,$>$\,4 quasar host galaxy of
 PSS J2322$+$1944,
which is also lensed into an Einstein ring configuration.
To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
that cover the full linewidth of $\sim$750\,\kms.

@@

Using the velocity dispersion ($\sigma$ = 30\,\kms) obtained by fitting a single Gaussian to the
de-lensed line profile of the companion and a
half-light radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from the best-fit lens model,  % redmost channel
we find a dynamical mass of
$M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun for the companion,
assuming an inclination angle of $i$\eq30$\degr$.
The uncertainty here only includes that of the CO source size.
On the other hand,
% we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
we find $M_{\rm dyn}$\,$\sin^2 30\degr$\,=\,5.8\E{8}\,\Msun
if we adopt the better-constrained $V$-band source size of $\sim$700\,pc \citepalias{Brewer08a}.
Since the $V$-band based dynamical mass measurement is substantially lower than the gas mass,
 the $V$-band emitting region may appear to be much smaller than its true extent due
to dust obscuration.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass, we find a galactic-scale %galaxy-wide
gas-to-dust ratio (GDR) of
40\pmm34.
This would be higher by a factor of two if we were to adopt a dust mass from the other SED fit that is unconstrained at 24\,$\micron$.
This GDR is lower than the statistical average of 206
in the \citetalias{Combes13a} sample but is well within the broad
range of values measured over their entire sample ($\sim$1$-$770).
Our ratio is also consistent with high-$z$ SMGs
% \citep[78\pmm26;][]{Bothwell13a}
\citep[]{Bothwell13a} and
local ULIRGs \citep{Wilson08a}, but lower than that of the Milky Way by
$\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.

@@

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.

@@

Fitting dust SED models to the IR-to-mm photometry, we derive
a lensing-corrected dust mass of $M_{\rm dust}$\ssim4\E{8}\,\Msun,
an infrared luminosity of \LIR$\sim$\,1.5\E{12}\,$(5.5/\mu_{\rm L})$\,\Lsun,
and a far-IR luminosity that corresponds to a SFR$_{\rm FIR}$\ssim120\,\sfrU.
These physical properties suggest that the merger system is dusty in nature with on-going \SF activity occuring
at a rate comparable to local ULIRGs/mergers and high-$z$ massive disk galaxies \citep{dacunha10a, Daddi10a}.
We also derive a stellar mass of $M_{*}$\ssim3\E{10}\,\Msun by fitting SED models to the
rest-frame UV-to-mm photometry, which have been corrected for their respective magnification factors before performing the fit to
account for differential lensing effect.
The source-plane distribution of the gas and stellar populations of different ages
indicates that the CO gas is of similar spatial extent as the old and long-lasting stellar populations,
whereas regions of recent \SF may be embedded within the molecular gas reservoir as a result of
gas accumulation driven by interactions with the companion.
Based on dynamical mass constraints, we cannot rule out the possibility that the
compact \SF in the host galaxy
may be heavily dust-obscured.
Hence, the true extent of recent \SF may be as extended as the molecular gas
reservoir.
While properties such as CO linewidth, SFR, and gas mass found in RXJ1131
are consistent with those of local ULIRGs and high-$z$ starburst galaxies,
its SFE is comparable to those of nearby and high-$z$ disk galaxies rather than
\SB systems. This is in good agreement with its disk-like kinematic signatures and its extended molecular gas distribution.
We find a specific \SF rate (sSFR\ssim4 Gyr\pmOne) that is $\lesssim$1.5$\sigma$ higher than those of ``main sequence'' galaxies.
The slight elevation in sSFR over the main sequence suggests that
the on-going star formation activity in RXJ1131 could be enhanced by interactions with the companion.
Recent simulations have illustrated that the disk component of a gas-rich
progenitor galaxy with low SFE can be
retained upon merging since the efficiency at removing angular momentum of the gas via
gravitational torques provided by stellar components is reduced in such a system \citep{Springel05a, Robertson06a, Hopkins09a}.
% and the gas rapidly reform a cold disc in the background.
As such, the extended gas disk of RXJ1131 together with its low SFE may indicate
that the \SF in RXJ1131 could form a
larger stellar bulge in the merger remnant upon coalescing.
